$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-10 paper/paper.tex
Go over the example derivation

The $\func{recv}$ process receives data along the channel with index $0$, thus that variable needs to be of type $\channel{t}{u}$.
After receiving twice, the process ends, so we should not be left with unused multiplicities: $u$ needs to be $\lz$.
We will use graded types to keep track of the exact number of times communication happens.
Whatever the input multiplicity of the channel, we will consume $2$ of it and leave the remaining as leftovers.
Once the types are given, the typing derivation is completely syntax directed.

The $\func{send}$ process sends data along the channel with index $0$, thus that variable needs to be of type $\channel{t}{u}$.
We instantiate the type of transmitted data $t$ to $\channel{\unit}{\func{\omega}}$, as that is something we can construct.
As by the type of the process $\func{recv}$, the transmitted multiplicities $u$ are $\lz$.
We will transmit once, thus using a single output multiplicity, and leave the rest as leftovers.

@@

We can now put these processes together and omit specifying the types of the channels that they share: Agda can infer them from the types of the processes.

>>>>

The $\func{recv}$ process receives data along the channel with index $0$, thus that variable needs to be of type $\channel{t}{u}$ for some $t$ and $u$.
After receiving twice, the process ends, and we should not be left with any unused multiplicities: $u$ needs to be $\lz$.
We will use graded types to keep track of the exact number of times communication happens.
Whatever the input multiplicity of the channel, we will consume $2$ of it and leave the remaining as leftovers.
Once the types are given, the typing derivation is completely syntax directed.

The $\func{send}$ process sends data along the channel with index $0$, thus that variable needs to be of type $\channel{t}{u}$ for some $t$ and $u$.
We instantiate $t$ (the type of data that we transmit) to $\channel{\unit}{\func{\omega}}$, as that is a value we can easily construct.
As per the type of the process $\func{recv}$, the transmitted multiplicities $u$ are $\lz$.
We will transmit once, thus using a single output multiplicity, and leave the rest as leftovers.

@@

We can now put these processes together.
Specifying the types of the channels is not required: Agda can infer them from the types of the processes.
